### 2020-05-07 paper.tex
Typo

One particular subject with more in-depth knowledge on RxJS described situations where they would have wished for tools which could ``understand'' the actual \mintinline{TypeScript}{Observable} graph better: (i) When an error is thrown within the function passed to an operator, the generated stack trace reflects where the operator called the function rather than the actual location where the function is implemented. (ii) In order to understand how data traverses through the graph, subjects augmumented code manually with the \mintinline{TypeScript}{tap}\footnote{\url{TODO}} operator to log values. A less invasive way would be preferable as stated.

>>>>

One particular subject with more in-depth knowledge on RxJS described situations where they would have wished for tools which could ``understand'' the actual \mintinline{TypeScript}{Observable} graph better: (i) When an error is thrown within the function passed to an operator, the generated stack trace reflects where the operator called the function rather than the actual location where the function is implemented. (ii) In order to understand how data traverses through the graph, subjects augmented code manually with the \mintinline{TypeScript}{tap}\footnote{\url{TODO}} operator to log values. A less invasive way would be preferable as stated.
